---
title: "Hw1"
output: html_document
---
```{r, echo = F}
data1 = read.csv('GSK.csv')
library(ggplot2)
```

the code chunk below will generate the average blood pressure by stress level
```{r,echo = F}
aggregate(sbp ~ stress, data = data1, mean)
```
The systolic blood pressures by stress level appear similar by standard deviation.
```{r, echo = F}
aggregate(sbp ~ stress, data = data1, sd)

```
The medium exercise level has the lowest age.
```{r, echo = F}
aggregate(age ~ exercise, data = data1, mean)
```
The Low exercise group differs the most with its mean.
```{r, echo = F}
aggregate(age ~ exercise, data = data1, sd)

```
As the level of education increases, average age tends to decrease, also the variance of the age tends to increase as the level of education increases.
```{r, echo = F}
boxplot(age ~ educatn, data = data1, horizontal = TRUE)
```

People who are married tend to have a higher variance in blood pressure than those who are not married.
```{r, echo = F}
ggplot(data1, aes(x=sbp, fill=married)) + geom_histogram(binwidth=2, alpha=.5, position="identity")
```
The medium exercise group tends to have the highest stress level.
```{r, echo = F}
two.way = table(data1$exercise,data1$stress)
mosaicplot(two.way, main = "Stress vs Exercise")
```

People who are married tend to have a higher proportion of lower stress levels
```{r, echo = F}
two.way = table(data1$married,data1$stress)
mosaicplot(two.way, main = "single or na")
```

The lowest exercise group has the highest number of people.

```{r, echo = F}
table(data1$exercise)
```
The medium stress group has the most amount of high education subjects
```{r, echo = F}
two.way = table(data1$stress,data1$educatn)
two.way
```

The medium stress group has the highest average age.
```{r, echo = F}
aggregate(age ~ stress, data = data1, mean)
```

Females tend to have a lower average systolic blood pressure.
```{r, echo = F}
aggregate(sbp ~ gender, data = data1, mean)

```

```{r, echo = F}
the.results = t.test(sbp ~ married, data = data1, var.equal = TRUE, level = 1-0.05)
pval = the.results$p.value
ts = round(the.results$statistic,4)
CI = round(the.results$conf.int,4)
```




```{r, echo = F}
pval
```
The test-statistic is:
```{r, echo = F}
ts
```
And the confidence interval is: 
```{r, echo = F}
CI
```
The difference of the average systolic blood pressure between married and non-married individuals is between -8.31 to 1.53.

We can reject the claim that married and non-married individuals tend to have differing systolic blood pressures, as their means tend to be similar to one another. Since the Pval is 17.59%, we can reject the alternative (that they are different) since there is not correlation between married and non-married with blood pressure.

```{r ref.label=knitr::all_labels(), echo = T, eval = F}
```

